\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage[tagged, highstructure]{accessibility}
\usepackage{bookmark}
\usepackage{enumitem}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    pdftitle={Week 2 - SQL Review},
    pdfauthor={Adrianna Holden-Gouveia},
    pdfsubject={Advanced Data - Lab Assignment},
    pdflang={en-US},
    pdfkeywords={SQL, queries, database, SQL Bolt, review}

}

% Configure PDF bookmarks for navigation
\bookmarksetup{
    numbered,
    open,
}

% Configure list spacing for better accessibility
\setlist{nosep}



\title{Week 2 - SQL Review}
\author{
        Adrianna Holden-Gouveia \\
        Website: \href{https://aholdengouveia.name}{aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
%        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        %\faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents


\section*{Accessibility Notice}
This document is also available in HTML format at:

Link: \href{https://aholdengouveia.name/AdvData/labs/week2.html}{\textbf{https://aholdengouveia.name/AdvData/labs/week2.html}}

The HTML version provides enhanced accessibility features including keyboard navigation, screen reader support, responsive design, dark mode support, and high contrast options.

\section*{Objectives:}
\begin{itemize}
    \item Demonstrate the use of some basic SQL queries
    \item Explain how SQL queries work, and practice using them
\end{itemize}
\section*{Complete the following problems}

References, a video, a PowerPoint and some notes are available at my website
Link: \href{https://www.aholdengouveia.name/AdvData/sqlpt1.html}{\textbf{https://www.aholdengouveia.name/AdvData/sqlpt1.html}}

The tutorial site we'll be using is Link: \href{https://sqlbolt.com/}{\textbf{https://sqlbolt.com/}}
We'll be going through several sections of this tutorial, go through the first 4 sections and the review

\subsection*{Please include}
    \begin{itemize}
        \item Screenshots of each section after you complete the challenges at the end.  Make sure you have the green checkmark on each problem.
        \item Which, if any, questions did you find challenging? Why?
        \item How many of the questions did you need a hint on? Why?
        \item What is your review of this tutorial? What would you change or fix?
    \end{itemize}



\section*{Deliverables}
A document with the answers to each question and all 5 screenshots. Make sure each screenshot has your name and term on it.
\end{document}