\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}


\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Database Documentation}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        %\faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents

\section*{Objectives:}
\begin{enumerate}
    \item Create some basic documentation for your database
\end{enumerate}
\section*{Complete the following problems}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/AdvData/databasedocumentation.html}

You should continue to use the dataset you've already chosen, that you made the schema for. If you need to pick a new dataset please email to discuss it with me

For this lab, you should start thinking about this data as if it was for an actual company.  What kind of company would want this data? What do they do? How do they make money? What is the size of the company?

\subsection*{Create your Documentation}

Based on the data you picked, come up with a company that might use this data.  This documentation should be for the company.  The company can be any size, just make note of what size you pick. Some of this you may have from previous labs, but you should work on organizing it into your documentation here. 

Your documentation can be done in any form you like, but if you're not sure consider using either MS Word or Google so that you can submit a PDF.  


    \begin{itemize}
        \item Type of company and a sentence or two about what they might be doing, how they might make money, any other information that might be helpful.
        \item ER diagram or Schema
        \item List of rules for the data, including if there are any data types that are preset (i.e. years always being an integer)
        \item Data dictionary
        \item Backup plans, including onsite, offsite, validity checks and frequency.
        \item Version Control plan, including initial suggestion of what to use.
        \item Documentation update plan including schedule for when you think  your documentation should be checked and why.  Likely to be annually or quarterly

    \end{itemize}



\section*{Deliverables}
\begin{enumerate}
    \item Document that includes answers to all the above questions.  Document is likely to be long enough you'll need some variety of index, or table of contents, or shortcuts to the data.  Your document needs to be sent in, you can also include a live link to a doc, but there must be a document uploaded that is static.  
\end{enumerate}
\end{document}