\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}


\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Query Optimization}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        %\faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents

\section*{Objectives:}
\begin{enumerate}
    \item Learn how to work with indexes
    \item Demonstrate how to add an index to a table to make it more efficient
\end{enumerate}
\section*{Complete the following problems}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/AdvData/optimization.html}


\subsection*{Query optimization practice on Kaggle}
    Go to \url{https://www.kaggle.com/learn/advanced-sql} and sign up for Kaggle, it's free, use any email you want.  If you are unfamiliar with the way kaggle works, there is a tutorial section, and an exercises section for this course. 
        \begin{itemize}
            \item Go through the Advanced SQL course. Take a screenshot of the completed course in your profile.  Make sure to include your name and the term in your screenshot.  This should show you completed the tutorials
            \item Now you'll be doing the exercises.  Go through the exercise on Query Optimization, it should be problems related to Pet Costumes International. Take a screenshot of your solution to both problems. Make sure to include your name and term in the screenshot.
        \end{itemize}




\subsection*{Query Optimization Challenges}
For each query make sure to include a short (1 paragraph or less) explanation of how you optimized it and solved the problem.  Each problem should also include your solution typed out, and a screenshot of your solution being run.  Make sure all screenshots include your name and the term.

Go to \url{https://www.sandboxsql.com/} and load in the database located here \url{https://github.com/aholdengouveia/aholdengouveia.github.io/blob/main/AdvData/labs/BooksDatabase.sqlite} for the following problems. 

Note: The queries don't always copy over well, especially symbols like the single quote.

    \begin{enumerate}
        \item On your database, if I give you the information on a book title, what is the command used to create an index to run the query more efficiently?
        \item Given the following query, which will select a book with a given title, what command would you use to create an index to make this query more efficient? 
        \begin{verbatim}
            SELECT authors.name, books.genre
            FROM books INNER JOIN authors 
            ON books.author_id = authors.author_id
            WHERE books.title = 'Dune' 
        \end{verbatim}
        \item Given the following query, which selects books from a table, create a command that will add an index based on genre.  Then give a new query that will show fantasy books only, making sure to use the index you created.
        \begin{verbatim}
            SELECT authors.name, books.genre
            FROM books INNER JOIN authors 
            ON books.author_id = authors.author_id 
        \end{verbatim}
    \end{enumerate}



\section*{Deliverables}
\begin{itemize}
    \item Document for the portion of this lab using Kaggle to practice query optimization and review your SQL. 
    \item Document for the challenges.  Each challenge should include the solution typed out, an explanation of how you arrived at your solution including any resources used, and a screenshot of the solution being run, each screenshot must include your name and the term. 

\end{itemize}
\end{document}