\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}


\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Big Data}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        %\faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents

\section*{Objectives:}
\begin{enumerate}
    \item Start to see how big data works and learn about some resources for further options
\end{enumerate}
\section*{Complete the following problems}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/AdvData/BigData.html}

\subsection*{Khan academy tutorial}

Go through the tutorial at \url{https://www.khanacademy.org/computing/ap-computer-science-principles/data-analysis-101}


    \begin{enumerate}
        \item Take a screenshot of your completed problems.  Make sure to include your name and term with each screenshot. 
        \item What did you think of this tutorial? Why?
        \item Would you recommend this tutorial to others? Why or why not?
        \item What do you think was missing from this tutorial?
    \end{enumerate}

\subsection*{Choose your own tutorial}

Pick one of the tutorials listed on this GitHub Repo \url{https://github.com/SkalskiP/courses}  If you already have some Python skill, you could do one of the tutorials at Kaggle \url{https://www.kaggle.com/learn/intro-to-machine-learning} instead.  

Please take note, there is a wide variety of options here, at all different skill levels and length.  You should pick a free one.  If you pick a longer option, you don't need to watch/do everything, just start it and do enough to get an idea of how it would go.


    \begin{enumerate}
        \item What did you think of this tutorial? Why?
        \item Would you recommend this tutorial to others? Why or why not? If there are specific circumstances or skills needed make sure to note that as well.
        \item How long was your selected tutorial? How long did you spend on it?
        \item Would you finish the tutorial if you had the time?
        \item What do you think was missing from this tutorial?
        \item What skills, if any, do you wish you had to understand this tutorial better?
    \end{enumerate}




\section*{Deliverables}
A document containing each of the screenshots clearly labelled with what they are.  Answers to all the questions, numbered and clearly labelled so it's obvious what you're answering.  
\end{document}