\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage[tagged, highstructure]{accessibility}
\usepackage{bookmark}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0}

% Configure PDF bookmarks for navigation
\bookmarksetup{
    numbered,
    open,
}
,
    pdftitle={Data Visualizations Lab},
    pdfauthor={Adrianna Holden-Gouveia},
    pdfsubject={Advanced Data - Lab Assignment},
    pdflang={en-US},
    pdfkeywords={data visualization, charts, graphs, AI visualization, data presentation}
}


\title{Data Visualizations}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
%        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        %\faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents


\section*{Accessibility Notice}
This document is also available in HTML format at:

\url{https://aholdengouveia.name/AdvData/labs/wk13dataviz.html}

The HTML version provides enhanced accessibility features including keyboard navigation, screen reader support, responsive design, dark mode support, and high contrast options.

\section*{Objectives:}
\begin{itemize}
    \item Learn how to create and evaluate data visualizations
\end{itemize}
\section*{Complete the following problems}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/AdvData/Datavis.html}

\subsection*{Use an AI to create some visuals}
Use an AI to create 3 visuals for the data you've been working with this term.  You'll be using the attached checklist to evaluate them.  For each of the 3 visualizations, please answer the following questions.
    \begin{enumerate}
        \item Why was this style (chart, graph, etc) picked do you think? 
        \item Do you think another would have been better? Why? 
        \item Using the checklist, evaluate the visualization on all 7 points.  If any points aren't relevant, make a note of why not.
        \item How does this data help illustrate a point? And what is the point of it?
        \item How much expertise in the data do you think someone would have to have for this visualization to be useful?
        \item What annotations are used, and are they the right ones? If no, what should have been used?
    \end{enumerate}

\subsection*{Create some visuals yourself}
Create 3 visuals for the data you've been working with this term.  You'll be using the attached checklist to evaluate them.  For each of the 3 visualizations, please answer the following questions.
    \begin{enumerate}
        \item Why was this style (chart, graph, etc) picked do you think? 
        \item Do you think another would have been better? Why? 
        \item Using the checklist, evaluate the visualization on all 7 points. If any points aren't relevant, make a note of why not.
        \item How does this data help illustrate a point? What point are you trying to illustrate?
        \item What annotations were used and why?
    \end{enumerate}



\section*{Deliverables}
A text document that contains the answers to both the AI created visuals and the ones you made yourself.  Make sure you are including the answers and checklist for EACH visualization. So there will be 6 sets of answers and 6 checklists in total. 
\end{document}