\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage[tagged, highstructure]{accessibility}
\usepackage{bookmark}
\usepackage{enumitem}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    pdftitle={Picking a Database Lab},
    pdfauthor={Adrianna Holden-Gouveia},
    pdfsubject={Advanced Data - Lab Assignment},
    pdflang={en-US},
    pdfkeywords={NoSQL, database selection, key-value store, document store, graph database}

}

% Configure PDF bookmarks for navigation
\bookmarksetup{
    numbered,
    open,
}

% Configure list spacing for better accessibility
\setlist{nosep}



\title{Picking a Database}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
%        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        %\faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents


\section*{Accessibility Notice}
This document is also available in HTML format at:

\url{https://aholdengouveia.name/AdvData/labs/wk9matchmaking.html}

The HTML version provides enhanced accessibility features including keyboard navigation, screen reader support, responsive design, dark mode support, and high contrast options.

\section*{Objectives:}
\begin{itemize}
    \item Learn how to evaluate database choices to pick the right one for a data set
\end{itemize}
\section*{Complete the following problems}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/AdvData/Databasematchmaking.html}

This should use the data set you've been working with.  If you need to change it for any reason please reach out to me.

You'll be evaluating different options for NoSQL databases for your data set. Each NoSQL option should have a pro/con list or table with at least 3 pros and 3 cons. Each option should also include a suggested vendor with a short paragraph explaining why you picked them. 

\subsection*{Please include}
    \begin{itemize}
        \item Short explanation of your data, what you're collecting or have collected, what other data you may want to collect in future, and any other important notes about your data. 
        \item Key value store
        \item Document store
        \item Graph
        \item Another NoSQL option of your choice.  Make sure it's not one of the ones you already did, it needs to be a totally different NoSQL type, not just a different vendor for one of the three types listed above. Some ideas if you're feeling stuck could include tuple store, triplestore, object or wide-column.
    \end{itemize}



\section*{Deliverables}
A text document that contains your database evaluations and overview of your data set.
\end{document}