\section{Initiatives}




\denseouterlist{

\entrymid[\textbullet]
{\textbf{No cost/Low Cost courses and OER}}{ }
{Participated in the no cost semester course with professional development and CIT to create courses that are no or low cost for the students. These Open Educational Resources (OER) allow students to start learning on day 1 without having to buy/rent books or software.  These free resources allow students to complete degrees more quickly, as well as reallocate resources to other venues such as more classes or technology needed.  All the courses I develop except one are done as low cost or no cost courses to ensure the best access for all students no matter what their situation is. This also includes ways to share courses outside of NECC such as on my personal website so that everyone can access my curriclum and materials.}


\entrymid[\textbullet]
{\textbf{Core Skills}}{ }
{Participated in the Core Skills workshops including the application and assignment creation for Core skills in a number of our CIS and CTN classes.  By participating frequently in the core skills workshops we are able to have core skills heavily integrated into all our technology degrees.  This not only allows for smoother graduation and advising for students, this also allows us to have more holistic curriculum.  I utilized the OER initiative and materials for all the courses I create (besides Advanced Security) so the curriculum I created is easy to share among my colleagues both full time and adjunct. These materials are put together using our Learning Management Tool, Blackboard, and including resources, labs and group work. Having core skills integrated so heavily into our courses from the ground up gives us the ability to smoothly integrate soft skills into our most technical courses, such as public presentation, writing skills and teamwork.}

\entrymid[\textbullet]
{\textbf{Zogotech}}{ }
{Heavily utilize Zogotech for data collection and analysis, as well as share knowledge with others, run reports and do target marketing for STEM students. Being able to use Zogotech after attending the workshops has allowed greater access to the STEM division so we can make data driven decisions for our courses and workshops.}

\entrymid[\textbullet]
{\textbf{Banner}}{ }
{Created small documentation sheets to share with other faculty members.  Being able to use banner has given the STEM division better access to register students for classes, smoothing out the retention between semesters and helping to make the continuation to graduation pathway as seamless as possible.  Being able to use Banner has helped to get more students registered faster, as well as make the students have less places they need to go to get ready for the next term.}

\entrymid[\textbullet]
{\textbf{Career Day}}{ }
{Organize and run career day for the CIS department every spring.  This day is focused on resume building, interview skills, elevator pitches and portfolios, as well as the other pieces of getting a job.  This is an event held every spring, but I also have some mini workshops and I schedule individual meetings to help prepare students for the job search process.}

\entrymid[\textbullet]
{\textbf{Integrated Student Experience}}{ }
{This committee is designed to implement the Integrated Student Experience (ISE) across the college for everything from the process of how a student starts, to the graduation process.  We're working on advising and how to get the students the best experience possible, how to make sure our diverse student body is evenly served on two campuses, and making sure that we're staying student centered and data driven with all our decision making.}

\entrymid[\textbullet]
{\textbf{Cybersecurity Training and Education Working Group}}{ }
{The Cybersecurity Training and Education Working Group's mission is to support the training and education of cybersecurity professionals in the Commonwealth through collaboration and partnerships. The leadership at MassCyberCenter hosts monthly meetings of the Working Group to update the group on initiatives, discuss requirements to support education and training, and provide opportunities for members to collaborate.}

\entrymid[\textbullet]
{\textbf{YouTube Channel}}{ }
{I created and maintain a YouTube channel that contains the videos I have created for classes.  I also include videos on request of students, such as how to write a technical resume, create a portfolio or even how to communicate professionally in the workplace.  The channel has playlists based on general topics or classes.  Videos are reviewed frequently do make sure the content and information is up to date and still relevant}

\entrymid[\textbullet]
{\textbf{Website}}{ }
{I created and maintain a website that contains the curriculum and extras I have created.  This website has the curriculum in a shareable way that includes videos, PowerPoints, notes, references, activities, hands-on lab work and sample syllabi.  It is designed to include the courses as well as other assistance such as how to get a technical job, and other student centric skills. The website is both open source and freely available for both students and teachers. I designed it to be easy to use if someone else also wanted to contribute to it, using version control so that anyone can use the framework.}

}