\section{Workshops}




\denseouterlist{

\entrymid[\textbullet]
{\textbf{Raspberry Pi}}{ }
{Workshop focused on the things you can make with a raspberry pi, mostly working with pre-built programs that the students could then edit.  We made a Magic Mirror that now lives in the STEM center, and a SelfieBot that comes to graduation and other large events.  The Magic mirror is a raspberry pi hooked up to a monitor that displays customizable information such as the weather, the school calendar and current news.  The SelfieBot is a robot that can take a picture (a selfie), it will then save the picture, print it on thermal paper and tweet out the picture with customizable hashtags.}

\entrymid[\textbullet]
{\textbf{Raspberry Pi}}{ }
{Workshop focused on the things you can make with a raspberry pi, mostly working with pre-built programs that the students could then edit.  We made a Magic Mirror that now lives in the STEM center, and a SelfieBot that comes to graduation and other large events.  The Magic mirror is a raspberry pi hooked up to a monitor that displays customizable information such as the weather, the school calendar and current news.  The SelfieBot is a robot that can take a picture (a selfie), it will then save the picture, print it on thermal paper and tweet out the picture with customizable hashtags.}

\entrymid[\textbullet]
{\textbf{3D printer}}{ }
{An introduction to 3D printing, basics of how to use CAD software, as well as slicing software to get the printer safely running.  Also how to use Octoprint so we can collect data about who is doing the printing, and create time lapses of the prints.}

\entrymid[\textbullet]
{\textbf{Intro to Soldering}}{ }
{Short workshop with soldering activity that can be easily added to any STEM week (STEM ed, Engineering week etc) with small badges that everyone who participates can make and bring home.  This workshop goes over soldering safety, as well as the basics of how to use a soldering iron, what you’d use one for, and what to do after you’ve created your badge.}

\entrymid[\textbullet]
{\textbf{Hacking the Vote}}{ }
{2020 Election - Created a video about the Right to Repair Ballot Question 1 in MA.  Working others at the college to encourage students to vote in my class and across the college.  Presentation dedicated to the security of voting machines.  Made for the 2016 election, but getting updated for the 2020 election.  Focused on the vulnerabilities in voting machines from the hardware up through the software. }

\entrymid[\textbullet]
{\textbf{Social Media}}{ }
{How to use social media, personal branding, how not to use social media and which social media to use depending on your goals. Looking at the best times of day to post, how to make eye catching posts, and the issues with using social media poorly and how that can not only reflect poorly on you, but also how social media can affect your ability to get or keep jobs in the future. How to work on your personal brand in terms of Search Engine Optimization (SEO) and putting your best foot forward. }



}
