\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}


\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Big Data}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        %\faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents

\section*{Objectives:}
\begin{enumerate}
    \item Students will gain a basic understanding of how to work through a problem using a larger dataset and some basic Machine Learning. 
\end{enumerate}
\section*{Complete the following}

Go to Kaggle \url{https://www.kaggle.com/} and create a free account.  

You will be going through the Titanic tutorial. \url{https://www.kaggle.com/code/alexisbcook/titanic-tutorial}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/IntroData/bigdata.html}

\subsection*{Please include Answers to the following questions}
    \begin{enumerate}
        \item What do you think of the tutorial?
        \item How difficult did you find this activity?
        \item Will you be trying another challenge on Kaggle? If yes, which one?
        \item Were you able to improve on the given code? 
        \item What was your accuracy?  (This might also show up as "score")
        \item Do you have any ideas on how you could improve that?


    \end{enumerate}



\section*{Deliverables}
A text document with the answers to the questions, and a screenshot of your submission onto the leaderboard. 
\end{document}