\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}


\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Data Visualization}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        \faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Lab work
%\end{abstract}
%\tableofcontents

\section*{Objectives:}
\begin{enumerate}
    \item The goal of this lab assignment is for students to distinguish between good and bad data visualizations using real-world examples. Through practical examples and observations, students will gain an understanding of when to use which data visualizations and how best to implement them.
\end{enumerate}
\section*{Complete the following problems}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/IntroData/datavis.html}

Examples of good Data Visualizations
\begin{itemize}
    \item Information is Beautiful \url{https://informationisbeautiful.net/}
    \item Storytelling with data \url{https://www.storytellingwithdata.com/blog}
\end{itemize}    

Examples of bad Data Visualizations
\begin{itemize}
    \item WTF Visualizations: Visualizations that make no sense \url{https://viz.wtf/}
    \item r/dataisugly \url{https://www.reddit.com/r/dataisugly/}
\end{itemize}

Using the guidelines from this website \url{https://web.archive.org/web/20230713094315/https://www.interaction-design.org/literature/article/guidelines-for-good-visual-information-representations#tufte%E2%80%99s_criteria_for_good_visual_information_representation-1} answer the following questions.  Make sure to use a table to breakdown your answer to ensure it hits each of the guidelines.

\subsection*{Answer the following questions}


    \begin{enumerate}
        \item What was your favorite Visualization? Why? 
        \item What was your least favorite Visualization? Or most aggravating Visualization?
        \item Which of the bad examples did you find most humorous? Why?
        \item From the good examples, pick one you like that you haven't already evaluated, we're going to look at the accessability of it. Name 3 ways you can make this visualization more accessible.  Create a narration of the visualization and an appropriate alt text.  Your narration can include a video.  One easy way to do this is create a screen capture video using something like OBS, and uploading it to a site like YouTube and making it unlisted so you can just share a link. 
        \item Go to \url{https://www.economist.com/graphic-detail}, do you think in general, this link belongs in the good or bad category? You don't need to evaluate every visualization, just look through the first page or two, and explain in a paragraph which one you think this link belongs in, why, and include screenshots of the visualizations you picked that support your opinion.
    \end{enumerate}


    \subsection*{Create your own Visualizations}
    \begin{enumerate}
        \item Going back to the Halloween candy data, pick 1 thing that you think would be better illustrated using a visualization.  Create your visualization using whatever software you like, this could be an online chart maker, or a spreadsheet or anything. 
        \item Explain why you picked that 1 thing, and explain how you decided which visualization to use and why.
        \item Go back to the data you collected/found and pick 2 things that you think would be better illustrated using a visualization. Create your visualization using whatever software you like, this could be an online chart maker, or a spreadsheet or anything. 
        \item Explain why you picked those 2 things from your data, and explain how you decided which visualization to use and why.
    \end{enumerate}

    \section*{Deliverables}
    \begin{enumerate}
        \item A text document with answers to  each of the above questions evaluating other people's visualizations
        \item A document that includes Screenshots (do not just upload multiple images to blackboard) of your 3 visualizations that you created.  Each screenshot should have the explanation of why below it.
    \end{enumerate}
\end{document}