\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}


\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{UI/UX and uses of data}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        \faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents

\section*{Objectives:}
\begin{itemize}
    \item Upon completion of this lab, participants will be able to critically assess the diverse applications of data in contemporary society and identify instances of misuse or abuse of data, thereby gaining a deeper understanding of the ethical and societal implications of data utilization
\end{itemize}


\section*{Resources needed for this lab}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.nameIntroData/usesofdata.html}

Examples of bad UI/UX
\begin{itemize}
    \item BadUI battles on reddit \url{https://www.reddit.com/r/badUIbattles/}
    \item Bad UI examples \url{https://goulartnogueira.github.io/BadUI/}
\end{itemize}    

Examples of good UI/UX
\begin{itemize}
    \item Webby Awards \url{https://www.webbyawards.com/}
    \item UX design awards \url{https://ux-design-awards.com/}
\end{itemize}


\subsection*{Answer the following questions}
Each of the above 4 websites showcases and best and the worst of UI/UX. Going through the entries/comments/winners/submissions please answer the following questions using the 10 point checklist and feedback pointers from \url{https://designlab.com/blog/design-critique-checklist-for-ux-designers#ten} Each answer should include these 10 points, if the point isn't relevant to your question, you may include an explanation of why instead. For example, if you want to critique a physical product, it may not have a navigation or mobile design to give feedback on, and it's ok to explain that

    \begin{enumerate}
        \item What was your favorite design?
        \item What was your least favorite design? Or most aggravating design?
        \item Which of the bad examples did you find most humorous?
        \item From the good example submissions, but not winners, who do you think should have won an award? And why?
    \end{enumerate}



\section*{Deliverables}
\begin{enumerate}
    \item A text document with answers to the each of the above questions, making sure to include the 10 point checklist for EACH answer.  You may do this in bullet points or a table.
    \item Find an article from the past year on a use of data that you consider bad or unethical, make sure the article is from a reputable source using the CRAAP test, and specific to a company/industry.
\end{enumerate}
\end{document}