\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Ethics Paper}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        \faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle



\section*{Objectives:}
\begin{enumerate}
    \item To do some research and thinking about an ethical issue in computer security. 
    \item Learn how to use a CRAP/CRAAP checklist for sources
\end{enumerate}
\section*{Ethics Paper Instructions}

References, a video, a PowerPoint and some notes are available at my website
\url {https://www.aholdengouveia.name/InfoSec/Ethics.html}

\subsection*{Select a topic either from below or choose something else you are interested in}
If you are choosing your own topic please check with me first.  You must pick a new topic if you've done this assignment before.  DO NOT just turn in a previously written paper.
        
    \begin{itemize}
        \item Social Justice/Hacktivism
        \item The ethics of "Hacking Back" (Retaliation by companies and governments when hacked)
        \item Encryption and backdoors for the government
        \item Government information sharing/tracking
        \item Algorithms used in the real world for things like job applications, personal reliability, social credit, etc.
        \item Tracking of people/purchases
        \item Privacy vs Security in the digital age (Personal privacy vs the need for security)
        \item Cyber Warfare (Including cyber arms control, civilian causalities and proportionality)
        \item Cybersecurity and Corporate responsibility (safeguarding customer data and preventing data breaches)
        \item Artificial intelligence (AI) in Cyber Security (can include Machine Learning or ML and algorithm)


    \end{itemize}

    

\section*{Reference information for CRAP/CRAAP}
    
    Turn in your report including your sources, you need at least 5, and a CRAP reliability checklist/paragraph for EACH  source. CRAP or CRAAP is used to define the quality of your sources. 
    \begin{itemize}

        \item You need at least 5 sources, and a CRAP reliability checklist/paragraph for EACH  source. 
        \item You may use either APA or MLA for your citations. If you want to use something else please just check with me first.
        \item Do not copy/paste from anywhere without citing your reference. Quoting or paraphrasing from a web site should include a citation.
        \item If you copy and paste into your paper, it is a quotation. It needs quotes and a link to the information (the link may be cut and paste from the address bar).
        \item If you use material that is only changed in minor ways (words or phrases omitted, shortened or slightly rearranged) it is a citation. It does not need quotes but does need a link to show from whence it came.
        \item If you take information from one source and substantially rephrase the material (paraphrase) it should be cited (show a link).
        \item Material drawn from multiple sources put in your own words does not need a direct citation but the sources would show up in any included bibliography.
         \item You can find instructions and more explanations for CRAP/CRAAP checklists at the following places
        \begin{itemize}
            \item CRAP test explanation 1 \url{ https://cccs.libguides.com/CRAPTest} or 
            \item CRAP test explanation 2 \url{https://libguides.butler.edu/c.php?g=117303&p=1940068} 
            \item Wikipedia explanation \url{https://en.wikipedia.org/wiki/CRAAP_test}
        \end{itemize}
    \end{itemize}    

    

\section*{Deliverables}

\begin{itemize}
    \item The report should be at least two pages not including citations, checklists, or anything besides actual content. Actual content should consist of:
        \begin{itemize}
            \item An explanation of each side of the problem. Be fair to the position of both sides.
            \item Present your own opinion on the ethical issues surrounding your topic and defend your viewpoint
            \item Find a news article related to the topic and include why it's relevant and a short summary of the article. 
            \item Describe how changes in technology will affect the issue.
        \end{itemize}
    \item Please submit a word doc or PDF of your file. 
    \item The report should include at least 5 references
    \item Your CRAP/CRAAP checklist for EACH of your 5 sources, but they should all be in the same document which can be different then the paper, or at the end of the paper
    \item A clearly labeled statement of the problem in a couple of sentences.

\end{itemize}

\end{document}