\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xurl}


\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Security Video Review}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        \faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents
  
\section*{Objectives:}
\begin{enumerate}
    \item Learning how to find new information and figure out something in security you're interested in.
\end{enumerate}
\section*{Complete the following problems}

%References, a video, a PowerPoint and some notes are available at my website
%\url {https://www.aholdengouveia.name}

\subsection*{Pick a video from one of the following conferences, video should be from the last couple years.}
\begin{enumerate}
    \item Def Con Safe Mode Presentations \url{https://media.defcon.org/DEF%20CON%2028/}
    \item Diana Initiative \url{https://www.youtube.com/c/TheDianaInitiative/videos}
    \item IntroSecCon \url{https://www.youtube.com/channel/UCx1Ektc73drCDq6W0tclZ8g} (Disclaimer:  I am one of the organizers for IntroSecCon and on their board)
\end{enumerate}
You can skim through videos to find one you're interested in, but if you find nothing is interesting you may pick another reputable security conference, but please check with me first. Answer the following questions about the video you picked
    \begin{enumerate}
        \item What video did you pick?
        \item Why did you pick it?
        \item Describe what your video is about in a short paragraph.
        \item Who's the presenter?
        \item What's their expertise?
        \item How did they do presenting?
        \item What's one thing you thought they did well presenting? Anything they could work on?
        \item What's one thing you learned in the video?
        \item Are you going to continue learning about this subject? Why or why not? 
        \item Would you recommend this video to others? Why it why not?
        \item Write a quick review of the video including a summary of your thoughts, include the link, the presenter and any other relevant info in the discussion.
        \item Watch one video someone else recommended. Do a short write up of what you thought about the video, why, and do you agree or disagree with the review they gave?
    \end{enumerate}



\section*{Deliverables}
Turn in a document with your answers and a link to your chosen video including title and presenter.  Add your video and requested info to the discussion.
\end{document}