\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Social Engineering}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        \faTwitter {: aholdengouveia} \\
        }

%S\date{\today}


\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents

As we are doing these activities please remember these rules.
\begin{enumerate}
    \item Don't make anyone feel victimized or targeted.
    \item Treat information gathered in an ethical manner. 
    \item Don't break any laws. 
    \item Don't abuse this knowledge. 
\end{enumerate}

    
    


\section*{Objectives:}
\begin{enumerate}
    \item Learn what social engineering is and why it's so important
    \item Learn some social engineering vocabulary
    \item Gain understanding on how social engineering works and how to protect against it
\end{enumerate}
\section*{Complete the following problems}

%References, a video, a PowerPoint and some notes are available at my website
%\url {https://www.aholdengouveia.name}

\subsection*{Please complete the following 3 activities}
    \begin{enumerate}
        \item Find and describe two real-world examples of social engineering attacks. Explain how these attacks exploited human behavior to compromise security. Use credible sources to support your examples.The examples can be in the news or observed in person, but make sure if it's from the news you include the articles referenced. Make sure to keep in mind your CRAP/CRAAP tests from previous assignments when evaluating sources
        \item Dominance Observation Games for Social Engineering: We know that the way someone greets you can tell a lot about whether they think they're dominant over you. For instance, when someone shakes your hand, if they turn their hand so that their hand is on top of yours during the shake, they're exhibiting dominance over you. Also, if they grab your upper arm while they're shaking your hand, or touch any part of your arm or body they are also exhibitingBe observant when greeting your friends and family members, take some notes. After you've made your list, observe these people throughout the day or evening. What other things do they do that fall in line with your original summation. dominance. If you don't have a safe way to do this with friends and family you should watch a video on something like YouTube, Netflix, Amazon, etc but watch at least 30min on mute for each conversation or listen to something in a language not your own, pay attention to what they are saying with their body language and facial expressions or tone if you're listening to something.   NO animated videos!  Pick some drama or comedy something with a lot of people talking.  Action won't work well for this. Try some of the Shakespeare or Jane Austen remakes like Pride and Prejudice or Hamlet. 
        \begin{itemize}
            \item Watch at least 3 conversations happening, you should watch from further away, you don't need to know what was said.
            \item 1 should be family members who you know well
            \item 1 should be strangers you don't know
            \item 1 can be of either variety
        \end{itemize}
        For each of the 3 conversations please take notes starting with the following questions:
        \begin{itemize}
            \item Was it a happy conversation? Sad? Tense?
            \item What led you to that conclusion?
            \item Who was dominant during the conversation?
            \item  What was the body language? Did dominance switch?
            \item What body language did you see happening?
            \item Could you see facial expressions? What did you see? What do you think those expressions mean?
        \end{itemize}
    
        
        \item Watch this video  \url{https://www.youtube.com/watch?v=uVc0latMWvY}    and answer the following questions:
        \begin{enumerate}
            \item What could have the student have done differently?
            \item What should they do in the future?
            \item How can they better protect himself against this sort of attack in the future?
            \item What are 2 resources you would recommend to this student?
        \end{enumerate}
          
        
    \end{enumerate}



\section*{Deliverables}
Turn in a document with answers to every question listed in the lab, including an analysis of the conversation you watched/listened to. Make sure you include details about why you think what you think about the conversation and sources for all your answers.  Even if you are pretty sure you know the answer make sure you include a source that agrees with you.
\end{document}