\documentclass[12pt]{article}

\usepackage{fontawesome}
\usepackage{hyperref}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}


\title{Sed}
\author{
        Adrianna Holden-Gouveia \\
        Website: \url{https://aholdengouveia.name}\\ 
        \date{\vspace{-5ex}}
        %Email: \href{mailto:admin@aholdengouveia.name}{admin@aholdengouveia.name} \\
        \faLinkedin{: aholdengouveia} \\
        \faGithub {: aholdengouveia} \\
        \faTwitter {: aholdengouveia} \\
        }




\begin{document}    

\maketitle

%\begin{abstract}
%This is a template for Linux Administration Lab work
%\end{abstract}
%\tableofcontents

%\section*{Objectives:}
%\begin{enumerate}
   % \item Objective 1
   % \item Objective 2
%\end{enumerate}
\section*{Complete the following problems}

\subsection*{Please include the command, a screenshot showing it works as intended, cite all sources you used, and give a short explanation of how the command works and why.}
    \begin{enumerate}
        \item Change the name Jo to Josephine
        \item Delete the last 5 lines.
        \item Print lines 3-15.
        \item Delete lines for people who live in California
        \item Print all lines where the birthdays are in the first week of the month.  Be careful of the dates for birthdays, the format is MM/DD/YY
        \item Append three asterisks (*) to the end of lines starting with Sir
        \item Replace the line containing "Westley Pirate" with the phrase "As you wish."  Make sure you replace the whole line not just the name
        \item Change Minerva McGonagall's birthday to 10/04/1935. Assume you don't know Minerva's original birthday. Use a regular expression to search for it.
        \item Delete all blank lines.
        \item Write a sed script that will  (actual sed script, NOT just the commands on the command line)
        \begin{enumerate}
            \item Insert above the first line the title  - Great Literary Characters -.
            \item Print the contents of the file with only the last name then the phone number.
            \item Append at the end of the file "Happily Ever after. The End"
        \end{enumerate}


    \end{enumerate}



\section*{Deliverables}
A text document with the grep statements used to get each result.  Clearly labeled so I can see which answer goes to which question.


Please include the command, a screenshot that includes the command and a few results showing it works as intended, cite all sources you used, and give a short explanation of how the command works and why. Make sure everything is in your own words.  Think of the explanation as you trying to walk someone through how to use sed when they haven't heard of it before.
\end{document}